%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\documentclass{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}  % Added for \href commands
\usepackage{ifthen}

\newcommand{\position}{TPM}
\newcommand{\company}{NHL}

% Define a macro to get the correct article
\newcommand{\getarticle}[1]{%
  \ifthenelse{
    \equal{\string\position}{A} \OR
    \equal{\string\position}{E} \OR
    \equal{\string\position}{I} \OR
    \equal{\string\position}{O} \OR
    \equal{\string\position}{U}
  } 
  {an}{a}%
}

\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Eric}{Crisp}{\urlstyle{same}{ecrisp@upenn.edu} | +1 (302) 528 - 2477 | \urlstyle{same}\href{https://linkedin.com/in/ecrisp}{linkedin.com/in/ecrisp}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyname{\company}
\vspace{0.5cm}
\companyaddress{	One Manhattan West \\
395 Ninth Avenue \\
New York City, NY }
\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear \company{}'s Hiring Team,}

\lettercontent{Thus far into my career, I have spent the majority of my time and effort engineering solutions to problems. It was only recently that I discovered my interest, skillset, and comfort leading technical projects.}

\lettercontent{The following sections contain responses to the questions posted for this position:}

\lettercontent{This position will be based in our New York City Office. Are you willing and able to commute to our office for this position? \\ 
\indent \bf{Yes, commute initially and likely relocate.}}

\lettercontent{If you are not currently living in the tri-state area, are you willing and able to relocate at your own expense for this position? \\ \indent \bf{Yes, I am living and would commute from Philadelphia}}

\lettercontent{Do you have the legal right to work in the United States? \\
\indent \bf{Yes.} }

\lettercontent{Will you now or in the future require visa sponsorship to continue work in the United States? \\
\indent \bf{No.}}

\lettercontent{What are your salary expectations for this role? (NOTE: We are NOT asking for your current salary or salary history) \\
\indent \bf{\$150,000.}}

\lettercontent{How did you hear about this position? Where did you first see this role posted? \\
\indent \bf{I indepdendently went looking for roles like this at the NHL and teams.}}

\lettercontent{Please give us an example of a technical product you’ve supported or led, including how you collaborated with engineering and stakeholders to ensure product quality and stability. \\
\indent \bf{ } }

\lettercontent{On a scale of 1-5 where 5 is the highest, how would you rate your ability to engage in technical discussions and translate technical concepts into business terms for non-technical stakeholders? \\
\indent \bf{4, I have been doing this process in various domains for years, translating those skills is a large part of why I am interested. Learning some of the technical domain specific to the role will require some degree of independent study, however, the underlying technical background exists and I am confident I can execute this role at the highest of standards.} }

\lettercontent{Tell us about a time when you had to lead or contribute to a major platform migration, app infrastructure improvement, or proof of concept involving new technology. What role did you play, and what was the outcome? \\
\indent \bf{The same pro.}}


\lettercontent{While my technical skills in this field may be in development, there are many aspects from my years in aerospace that bring unique value to the table. During my first year at Firefly Aerospace, I collaborated with two other engineers to design, build, and test a new engine that would go on to successfully land on the moon in 2025. Throughout this project, I gained invaluable experience not only in various technical skills but also in all aspects of the product development cycle, developing relationships with and communicating results to stakeholders, balancing trade studies with both decisiveness and justification, and seeing an open ended technical project to competition. On day one at Blue Origin, I was individually tasked with turning a large-scale, hypothetical business idea into a reality; within four months, I had developed the RTM (real time model) - a software product that achieved the stated goal and continues to excel to this day. As the scope accelerated and the product value grew, I had the opportunity to lead engineers, manage the product development, and develop new technical and non-technical skills along the way.}


\lettercontent{Among the most valuable assets I bring to the table is not a skill at all, but an intangible quality - genuine passion. It's as simple as this, to me, as ubiquitous as AI is and will continue to become, the impact on the lives of countless impressionable individuals across all walks of life are inherently dependent on the quality of the products released and therefore need to be unequivocally ethical, safe, and robust. This passion is what motivated me to leave my career in aerospace and pursue a new career; one that hopefully starts right here at the \company{}, as \getarticle{\position} \position{}.} 

% \vspace{0.1cm}
\closing{Sincerely}{Eric Crisp}
\end{document}